TrenchR: an R package for transparent environmental and ecological biophysics

### 2020-10-06 Manuscript_full.Rmd
Minor fixes

---
title: 'TrenchR: an R package for transparent environmental and ecological biophysics'
author: "Lauren B. Buckley, Bryan Briones Ortiz, Aji John, Ofir Levy, Yutaro Sakairi"
date: "February 4, 2020"
output: html_document
---

@@

We estimate convective heat exchange between the animal and surrounding air using ithe following relationship:
$$Q_{conv}= ef*H_L*(A*proportion)*(T_a-T_b),$$
where an enhancement factor, $ef$, multiplier can be incorported to account for increases in heat exchange resulting from air turbulance in field conditions

@@

We assume, as in generally done for lizards, that heat exchange associated with metabolism and evaporation is negliglible:
```{r}
Qmet= 0
Qevap= 0
```

@@

We also implement a similiar but simplied energy balance. The energy balance omits conduction with the ground and thus underestimates temperatures, but we implement it for comparison purposes:
```{r}
Te2= rep(NA, 24)
for(hr in 1:24) Te2[hr]= Tb_CampbellNorman(T_a=Ta[hr]+273.15, S=Qabs[hr]/svl, epsilon=epsilon_s, c_p=29.3, D=svl, V=V)
#CHECK
```

@@

Te4= rep(NA, 24)
for(hr in 1:24) Te4[hr]= Tb_Fei(TAH=Ta[hr]+273.15, T_s=Ts[hr]+273.15, T_a=Ts[hr]+273.15, UDT=Qabs[hr], GLW=Qabs[hr],  shade=0)
#FIX UDT?

>>>>

---
title: 'TrenchR: an R package for transparent environmental and ecological biophysics'
author: "Lauren B. Buckley, Bryan Briones Ortiz, Aji John, Ofir Levy, Yutaro Sakairi"
date: "February 4, 2020"
output:
  pdf_document: default
  html_document: default
---

@@

We estimate convective heat exchange between the animal and surrounding air using ithe following relationship:
$$Q_{conv}= ef*H_L*(A*proportion)*(T_a-T_b),$$
where an enhancement factor, $ef$, multiplier can be incorporated to account for increases in heat exchange resulting from air turbulance in field conditions

@@

We assume, as in generally done for lizards, that heat exchange associated with metabolism and evaporation is negligible:
```{r}
Qmet= 0
Qevap= 0
```

@@

We also implement a similar but simplified energy balance. The energy balance omits conduction with the ground and thus underestimates temperatures, but we implement it for comparison purposes:
```{r}
Te2= rep(NA, 24)
for(hr in 1:24) Te2[hr]= Tb_CampbellNorman(T_a=Ta[hr]+273.15, S=Qabs[hr]/svl, epsilon=epsilon_s, c_p=29.3, D=svl, V=V)
#CHECK
```

@@

Te4= rep(NA, 24)
for(hr in 1:24) Te4[hr]= Tb_Fei(T_a=Ta[hr]+273.15, T_g=Ts[hr]+273.15, H=Qabs[hr], lw=Qabs[hr], shade=0, m=mass, Acondfact =0.1, Agradfact =0.3)
#CHECK
